Reanalysis Step 9: Alternative Propensity Score Specifications

### 2025-09-05 reanalysis-9-alternative_specifications.qmd
debug

# Define which methods to actually run
# Comment out any methods you want to skip
methods_to_run <- c(
  "nearest_glm",
  "nearest_gam", 
  "nearest_gbm",
  "nearest_lasso",
  "nearest_rpart",
  "nearest_mahalanobis",
  "subclass_glm",
  "cbps",
  "entropy",
  "bart",
  "twang_gbm"  # Will load from reanalysis-4 if available
)

log_message(paste0("Will run ", length(methods_to_run), " methods"))
```

>>>>

# Define all available methods
all_methods <- c(
  "nearest_glm",
  "nearest_gam", 
  "nearest_gbm",
  "nearest_lasso",
  "nearest_rpart",
  "nearest_mahalanobis",
  "subclass_glm",
  "cbps",
  "entropy",
  "bart",
  "twang_gbm"  # Will load from reanalysis-4 if available
)

# Define completed methods (add to this list as methods complete successfully)
completed_methods <- c(
  "nearest_glm"  # Uncomment if completed
)

# Methods to run = all methods minus completed ones
methods_to_run <- setdiff(all_methods, completed_methods)

# Optionally, you can also explicitly exclude problematic methods
methods_to_exclude <- c(
  # Add any methods that consistently fail or you want to skip
)
methods_to_run <- setdiff(methods_to_run, methods_to_exclude)

log_message(paste0("Will run ", length(methods_to_run), " methods"))
if (length(completed_methods) > 0) {
  log_message(paste0("Skipping completed: ", paste(completed_methods, collapse = ", ")))
}
```
